Draft

### 2020-04-04 SubGroup.Rmd
update

@@

Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
# Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)

@@

CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")

SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
# rm(list=(ls()))
```

```{r AUC}
## All

@@

ROCPRC <- function(dataset, dataset_long){
  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))

@@

  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
  aucT3 <- c("Lunit INSIGHT CXR  ", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
  aucT4 <- c("JF CXR-1 ", round(attr$auc[4],3))

@@

l <- ROCPRC(MDF, MDF_long)
all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
all$subgroup <- "all"

## New only
l <- ROCPRC(New, New_long)
New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
New$subgroup <- "New cases"

## Old only
l <- ROCPRC(Old, Old_long)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

## Young
l <- ROCPRC(Young, Young_long)
Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Young$subgroup <- "Young age"

## Middle
l <- ROCPRC(Middle, Middle_long)
Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Middle$subgroup <- "Middle age"

## Senior
l <- ROCPRC(Senior, Senior_long)
Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Senior$subgroup <- "Old age"

## Referral only
l <- ROCPRC(Referral, Referral_long)
Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Referral$subgroup <- "Referred"

## DOTS only
l <- ROCPRC(DOTS, DOTS_long)
DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
DOTS$subgroup <- "DOTS retested"

## Walk-in only
l <- ROCPRC(WalkIn, WalkIn_long)
WalkIn <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
WalkIn$subgroup <- "WalkIn"

# ## Missing 
# l <- ROCPRC(Missing, Missing_long)
# Missing <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Missing$subgroup <- "Missing"

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))

@@

@@

tiff("Results/AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
require(gridExtra)
grid.arrange(age, referral, history, agePC, referralPC, historyPC, ncol=3)

dev.off()
rm(age, referral, history, agePC, referralPC, historyPC)
```

>>>>

Female <- MDF[MDF$Gender %in% "F", ]
Male <- MDF[MDF$Gender %in% "M", ]

@@

Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
# 
# 
# New_Yong <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[15,25)",]
# Old_Yong <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[15,25)",]
# 
# New_Middle <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[25,60)",]
# Old_Middle <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[25,60)",]
# 
# New_Senior <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[60,108]",]
# Old_Senior <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[60,108]",]

# Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)

@@

# CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
# CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
# CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
# CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
# CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
# CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
# CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
# CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
# 
# 
# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
# rm(list=(ls()))
```

```{r 2 AUC}
## All

@@

ROCPRC <- function(dataset){
  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))

@@

  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
  aucT4 <- c("JF CXR-1", round(attr$auc[4],3))

@@

l <- ROCPRC(MDF)
all <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
all$subgroup <- "all"

## New only
l <- ROCPRC(New)
New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
New$subgroup <- "New cases"

## Old only
l <- ROCPRC(Old)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

## Young
l <- ROCPRC(Young)
Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Young$subgroup <- "Young age"

## Middle
l <- ROCPRC(Middle)
Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Middle$subgroup <- "Middle age"

## Senior
l <- ROCPRC(Senior)
Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Senior$subgroup <- "Old age"

## Referral only
l <- ROCPRC(Referral)
Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Referral$subgroup <- "Referred"

## DOTS only
l <- ROCPRC(DOTS)
DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
DOTS$subgroup <- "DOTS retested"

## Walk-in only
l <- ROCPRC(WalkIn)
WalkIn <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
WalkIn$subgroup <- "WalkIn"

## Female
l <- ROCPRC(Female)
Female <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Female$subgroup <- "Female"

## Male
l <- ROCPRC(Male)
Male <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Male$subgroup <- "Male"
#### stratification by age AND prior TB history

# l <- ROCPRC(New_Yong)
# New_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Yong$subgroup <- "New_Yong"
# 
# 
# l <- ROCPRC(New_Middle)
# New_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Middle$subgroup <- "New_Middle"
# 
# 
# l <- ROCPRC(New_Senior)
# New_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Senior$subgroup <- "New_Senior"
# 
# 
# 
# l <- ROCPRC(Old_Yong)
# Old_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Yong$subgroup <- "Old_Yong"
# 
# 
# l <- ROCPRC(Old_Middle)
# Old_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Middle$subgroup <- "Old_Middle"
# 
# 
# 
# l <- ROCPRC(Old_Senior)
# Old_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Senior$subgroup <- "Old_Senior"
# 
# 
# temp <- rbind(New_Yong, New_Middle, New_Senior, Old_Yong, Old_Middle, Old_Senior)
# colnames(temp) <- c("DL.System", "AUC", "PCAUC", "Subgroup")
# temp$AUC <- as.numeric.factor(temp$AUC)
# temp$PCAUC <- as.numeric.factor(temp$PCAUC)

# View(temp)

# ggplot(temp, aes(x=DL.System, y=AUC, fill=Subgroup))+  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))
```

```{r ROC AUC with CI}

library(pROC)
ROC <- function(dataset){
  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, dataset)
  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)

  aucT <- as.data.frame(matrix(c(roc_CAD6[2], roc_CAD6[1], roc_CAD6[3], roc_qure[2], roc_qure[1], roc_qure[3], roc_Lunit[2], roc_Lunit[1], roc_Lunit[3], roc_JF1[2], roc_JF1[1], roc_JF1[3], roc_IF2[2], roc_IF2[1], roc_IF2[3]),  byrow=TRUE, ncol =  3))
  names(aucT) <- c("AUC", "AUCL", "AUCH")
  aucT$DL.System <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")

  return(aucT)
}

## New only
New <- ROC(New)
New$subgroup <- "New cases"

## Old only
Old <- ROC(Old)
Old$subgroup <- "Previously treated cases"

## Young
Young <- ROC(Young)
Young$subgroup <- "Young age"

## Middle
Middle <- ROC(Middle)
Middle$subgroup <- "Middle age"

## Senior
Senior <- ROC(Senior)
Senior$subgroup <- "Old age"

## Referral only
Referral <- ROC(Referral)
Referral$subgroup <- "Referred"

## DOTS only
DOTS <- ROC(DOTS)
DOTS$subgroup <- "DOTS retested"

## Walk-in only
WalkIn <- ROC(WalkIn)
WalkIn$subgroup <- "WalkIn"

ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
View(ROCaucTable)
write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)

@@

gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

@@

genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

tiff("Results/PRC ROC AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
require(gridExtra)

grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
# grid.arrange(age, referral, history, ncol=3)

dev.off()
# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)

tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
dev.off()

```{r}
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
### AUC
age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

tiff("Results/ROC_AUC plot.tif", width = 13, height = 3, units = "in", res = 100)
require(gridExtra)

grid.arrange(age, referral, history, ncol=3)

dev.off()
rm(age, referral, history)
```
